### 2013-03-28 doc/sosp13/tasks.tex
reference to sample code
ct

\paragraph{Tasks} 
Tasks are specified with a ``functor'' object that holds both code to execute and initial state. The functor can be specified with a function pointer and explicit arguments, a C++ struct that overloads the parentheses operator, or a C++11 lambda. These objects, typically very small (on the order of 64 bytes), hold read-only values such as an iteration index and pointers to common data or synchronization objects. These task functors can be serialized and transported around the system, and eventually executed by a Worker, as described next.

@@

>>>>

\paragraph{Tasks} 
Tasks are specified with a ``functor'' object that holds both code to execute and initial state. The functor can be specified with a function pointer and explicit arguments, a C++ struct that overloads the parentheses operator, or a C++11 lambda. These objects, typically very small (on the order of 64 bytes), hold read-only values such as an iteration index and pointers to common data or synchronization objects. These task functors can be serialized and transported around the system, and eventually executed by a worker, as described next.

@@

Figure~\ref{fig:sample} shows sample code using \Grappa for a parallel tree
search. The important aspect to note is that the code looks very similar to
what would be written for single shared-memory system, without any concern about data locality or communication.
